---
title: "Defendars"
author: "Parsa Moghaddam"
date: '2023-04-01'
output: html_document
---

```{r, include=FALSE, warning=FALSE}
library(readxl)
library(dplyr)
library(corrplot)
library(tidyverse)
```

# Reading Data

```{r}
fifa2023 <- read.csv("fifa2023.csv")
EN2022 <- read.csv("2021-2022_EN.csv")
SP2022 <- read.csv("2021-2022_SP.csv")
IT2022 <- read.csv("2021-2022_IT.csv")
FR2022 <- read.csv("2021-2022_FR.csv")
GE2022 <- read.csv("2021-2022_GE.csv")
```




```{r}
fifa2023 <- fifa2023[c("Known.As", "Full.Name", "Overall", "Nationality")]

fifa2023 <- fifa2023 %>% 
    rename (
        name = Full.Name
    )

dfAll <- rbind(EN2022, SP2022, IT2022, FR2022, GE2022)

dfAll <- dfAll %>%
    rename(
        name = Player
    )

merged <- merge(fifa2023, dfAll, by = "name")
merged$Squad <- factor(merged$Squad)
merged$League <- factor(merged$League)
```


# Defendars Data

```{r}
defendars <- merged[merged$Pos == "DF", ]
defendars2 <- merged %>% filter(Pos == "DF", )

defendars$SM = 0

for(i in 1:588){
  defendars$SM[i] = (defendars2$Starts[i] / defendars2$MP[i])
}

# Players tackled percent
defendars$TKWON = 0

for(i in 1:588){
  defendars$TKWON[i] = (defendars2$TklW[i] / defendars2$Tkl[i])
}

#Dribbles TAckled percent
defendars$TKCWON = (defendars$Tkl./100)
```


# Simple Model W/O SM

```{r}
simple <- lm(Overall ~ Ast + TKCWON + Blocks , data = defendars)
summary(simple)
```

#Simple Model with SM

```{r}
simple <- lm(Overall ~ Ast + TKCWON + Blocks + SM, data = defendars)
summary(simple)
```

#Simple Model with SM and Astper90

```{r}
simple2 <- lm(Overall ~ Ast_per90 + TKCWON + Blocks + SM, data = defendars)
summary(simple2)
```





# fixed effect for Squad w/o SM

```{r}
m1 <- lm(Overall ~  Ast + TKCWON + Blocks + Squad-1, data = defendars)
summary(m1)
```

# fixed effect for Squad with SM

```{r}
m1 <- lm(Overall ~  Ast + TKCWON + Blocks + SM + Squad-1, data = defendars)
summary(m1)
```



```{r}
fe_coefs4 <- summary(m1)$coefficients
fe_coefs4 <- as.data.frame(fe_coefs4)
fe_coefs4[order(fe_coefs4$Estimate, decreasing = TRUE),]
```


```{r}
model1 <- lm(Overall ~  Ast_per90 + TKCWON + Blocks + SM + Squad-1, data = defendars)
summary(model1)
```



```{r}
fe_coefs4 <- summary(model1)$coefficients
fe_coefs4 <- as.data.frame(fe_coefs4)
fe_coefs4[order(fe_coefs4$Estimate, decreasing = TRUE),]
```





# fixed effect for League w/o SM

```{r}
m2 <- lm(Overall ~ Ast + TKCWON + Blocks + League-1, data = defendars)
summary(m2)
```


# fixed effect for League with SM

```{r}
m2 <- lm(Overall ~ Ast + TKCWON + Blocks + SM + League-1, data = defendars)
summary(m2)
```


```{r}
fe_coefs4 <- summary(m2)$coefficients
fe_coefs4 <- as.data.frame(fe_coefs4)
fe_coefs4[order(fe_coefs4$Estimate, decreasing = TRUE),]
```


```{r}
model2 <- lm(Overall ~ Ast_per90 + TKCWON + Blocks + SM + League-1, data = defendars)
summary(model2)
```


```{r}
fe_coefs4 <- summary(model2)$coefficients
fe_coefs4 <- as.data.frame(fe_coefs4)
fe_coefs4[order(fe_coefs4$Estimate, decreasing = TRUE),]
```







# Fixed Effects for League and Club w/o SM

```{r}
m3_1 <- lm(Overall ~ TKCWON + Blocks + Ast + League-1 + Squad-1, data = defendars)
summary(m3_1)
```


# Fixed Effects for League and Club with SM

```{r}
m3 <- lm(Overall ~ Ast + TKCWON + Blocks + SM + League-1 + Squad-1, data = defendars)
summary(m3)
```


```{r}
fe_coefs4 <- summary(m3)$coefficients
fe_coefs4 <- as.data.frame(fe_coefs4)
fe_coefs4[order(fe_coefs4$Estimate, decreasing = TRUE),]
```


# FINAL MODEL

```{r}
model3 <- lm(Overall ~ Ast_per90 + TKCWON + Blocks + SM + League-1 + Squad-1, data = defendars)
summary(model3)
```



```{r}
fe_coefs4 <- summary(model3)$coefficients
fe_coefs4 <- as.data.frame(fe_coefs4)
fe_coefs4[order(fe_coefs4$Estimate, decreasing = TRUE),]
```


```{r}
which(predict(model3) > 87)
max(model3$fitted.values)
```


```{r}
model33 <- lm(Overall ~  TKCWON + Blocks + SM + League-1 + Squad-1, data = defendars)
summary(model33)
```

```{r}
which(predict(model33) > 86)
max(model33$fitted.values)
```


#Model using tackle instead of tackle percentage won!

```{r}
m3_2 <- lm(Overall ~ Tkl + Blocks + SM + Ast + League-1 + Squad-1, data = defendars)
summary(m3_2)
```


#Model using tackle instead of tackle percentage won and no SM / Assist!

```{r}
m3_3 <- lm(Overall ~ Tkl + Blocks + League-1 + Squad-1, data = defendars)
summary(m3_3)
```




#Model using tackle instead of tackle percentage won and no assist!

```{r}
m10 <- lm(Overall ~ Tkl + Blocks + SM + League-1 + Squad-1, data = defendars)
summary(m10)
```



```{r}
#model with tackle + no SM
hist(predict(m3_3), main="Rating Distribution", xlab="Rating")

#model with tackle perc + SM
hist(predict(model3), main = "Rating Distribution", xlab = "Rating")
```




```{r}
#model with tackle + no Assist
hist(predict(m10), main="Rating Distribution", xlab="Rating")

#model with tackle perc + SM
hist(predict(m3), main = "Rating Distribution", xlab = "Rating")
```


```{r}
#model with tackle + no Assist
hist(predict(m10), main="Rating Distribution", xlab="Rating")

#model with tackle perc + SM
hist(predict(model3), main = "Rating Distribution", xlab = "Rating")
```


# HEREEEEEEEE

```{r}
#Model with tackles
plot(m3_3$residuals ~ m3_3$fitted.values, xlab = "Predicted Ratings", ylab = "Residual", data = defendars)
abline(h = 0)

#model with tackle perc + SM
plot(model3$residuals ~ model3$fitted.values, xlab = "Predicted Ratings", ylab = "Residual", data = defendars)
abline(h = 0)

```










```{r}
#Model with tackles
plot(m3_3$residuals ~ m3_3$fitted.values, xlab = "Predicted Ratings", ylab = "Residual", data = defendars)
abline(h = 0)

#model with tackle perc + SM
plot(m3$residuals ~ m3$fitted.values, xlab = "Predicted Ratings", ylab = "Residual", data = defendars)
abline(h = 0)

```




```{r}
plot(predict(m3_3),
    defendars$Overall,
    xlab = "Predicted Values",
    ylab = "Observed Values"
)
abline(
    a = 0,
    b = 1,
    col = "red",
    lwd = 2
)
```


# Full model (same length)

```{r}
#m3_3 <- lm(Overall ~ Tkl + Blocks + League-1 + Squad-1, data = defendars)

fit <- lm(Overall ~ Ast_per90 + (defendars$TklW / defendars$Tkl) + (defendars$Starts / defendars$MP) + Blocks + League-1 + Squad-1, data = defendars)
length(fit$fitted.values)
```


```{r}
plot(predict(fit),
    defendars$Overall,
    xlab = "Predicted Values",
    ylab = "Observed Values"
)
abline(
    a = 0,
    b = 1,
    col = "red",
    lwd = 2
)
```



