---
title: "c45Project"
author: "Parsa Moghaddam"
date: '2023-03-24'
output: html_document
---


```{r}
library(readxl)
library(dplyr)
library(corrplot)
library(tidyverse)
```



```{r}
fifa2023 <- read.csv("fifa2023.csv")
EN2022 <- read.csv("2021-2022_EN.csv")
SP2022 <- read.csv("2021-2022_SP.csv")
IT2022 <- read.csv("2021-2022_IT.csv")
FR2022 <- read.csv("2021-2022_FR.csv")
GE2022 <- read.csv("2021-2022_GE.csv")
```




```{r}
fifa2023 <- fifa2023[c("Known.As", "Full.Name", "Overall", "Nationality")]

fifa2023 <- fifa2023 %>% 
    rename (
        name = Full.Name
    )

dfAll <- rbind(EN2022, SP2022, IT2022, FR2022, GE2022)

dfAll <- dfAll %>%
    rename(
        name = Player
    )
```


```{r}
merged <- merge(fifa2023, dfAll, by = "name")
merged$Squad <- factor(merged$Squad)
merged$League <- factor(merged$League)
```



```{r}
forwards <- merged[merged$Pos == "FW" | merged$Pos == "FWMF" | merged$Pos == "MFFW", ]
forwards2 <- merged %>% filter(Pos == "FW" | merged$Pos == "FWMF" | merged$Pos == "MFFW", )
```


```{r}
lm.fit <- lm(Overall ~ Gls+Ast, data = forwards2)
summary(lm.fit)
```






```{r}
fe_lm.fit <- lm(Overall ~ Gls + Ast + xG + Min + Squad-1, data = forwards2)
summary(fe_lm.fit)
```




```{r}
fe_coefs <- summary(fe_lm.fit)$coefficients
fe_coefs <- as.data.frame(fe_coefs)
fe_coefs[order(fe_coefs$Estimate, decreasing = TRUE), ]
```



```{r}
fe_lm.fit2 <- lm(Overall ~ Gls + Ast + xG + Min + League-1, data = forwards2)
summary(fe_lm.fit2)
```


```{r}
forwards2$SM = 0

for(i in 1:616){
  forwards2$SM[i] = (forwards2$Starts[i] / forwards2$MP[i])
}

fe <- lm(Overall ~ Gls + Ast + xG  + Min + SM + League-1 + Squad-1, data = forwards2)
summary(fe)
```









```{r}
fe <- summary(fe)$coefficients
fe <- as.data.frame(fe)
fe[order(fe$Estimate, decreasing = TRUE),]
```


# Benzema is highest rated attacker with rating of 95!























# Defendars:

```{r}
defendars <- merged[merged$Pos == "DF", ]
defendars2 <- merged %>% filter(Pos == "DF", )

defendars$SM = 0

for(i in 1:587){
  defendars$SM[i] = (defendars2$Starts[i] / defendars2$MP[i])
}

# Players tackled percent
defendars$TKWON = 0

for(i in 1:587){
  defendars$TKWON[i] = (defendars2$TklW[i] / defendars2$Tkl[i])
}

#Dribbles TAckled percent
defendars$TKCWON = (defendars$Tkl./100)
```








# Simple Model W/O SM

```{r}
simple <- lm(Overall ~ Ast + TKCWON + Blocks , data = defendars)
summary(simple)
```



#Simple Model with SM

```{r}
simple <- lm(Overall ~ Ast + TKCWON + Blocks + SM, data = defendars)
summary(simple)
```




# fixed effect for Squad w/o SM

```{r}
m1 <- lm(Overall ~  Ast + TKCWON + Blocks + Squad-1, data = defendars)
summary(m1)
```

# fixed effect for Squad with SM

```{r}
m1 <- lm(Overall ~  Ast + TKCWON + Blocks + SM + Squad-1, data = defendars)
summary(m1)
```


```{r}
fe_coefs4 <- summary(m1)$coefficients
fe_coefs4 <- as.data.frame(fe_coefs4)
fe_coefs4[order(fe_coefs4$Estimate, decreasing = TRUE),]
```




# fixed effect for League w/o SM

```{r}
m2 <- lm(Overall ~ Ast + TKCWON + Blocks + League-1, data = defendars)
summary(m2)
```


# fixed effect for League with SM

```{r}
m2 <- lm(Overall ~ Ast + TKCWON + Blocks + SM + League-1, data = defendars)
summary(m2)
```


```{r}
fe_coefs4 <- summary(m2)$coefficients
fe_coefs4 <- as.data.frame(fe_coefs4)
fe_coefs4[order(fe_coefs4$Estimate, decreasing = TRUE),]
```




# Fixed Effects for League and Club w/o SM

```{r}
m3_1 <- lm(Overall ~ TKCWON + Blocks + Ast + League-1 + Squad-1, data = defendars)
summary(m3_1)
```



# Fixed Effects for League and Club with SM

```{r}
m3 <- lm(Overall ~ Ast + TKCWON + Blocks + SM + League-1 + Squad-1, data = defendars)
summary(m3)
```













```{r}
fe_coefs4 <- summary(m3)$coefficients
fe_coefs4 <- as.data.frame(fe_coefs4)
fe_coefs4[order(fe_coefs4$Estimate, decreasing = TRUE),]
```




# Roberston is highest rated when Asissts is in model

```{r}
max(m3$fitted.values)
m3$fitted.values
```





#Model using tackle instead of tackle percentage won!

```{r}
m3_2 <- lm(Overall ~ Tkl + Blocks + SM + Ast + League-1 + Squad-1, data = defendars)
summary(m3_2)
```


#Model using tackle instead of tackle percentage won and no SM!

```{r}
m3_3 <- lm(Overall ~ Tkl + Blocks + Ast + League-1 + Squad-1, data = defendars)
summary(m3_3)
```


#Histogram to show rating distr


```{r}
#model with tackle + no SM
hist(predict(m3_3), main="Rating Distribution", xlab="Rating")

#model with tackle perc + SM
hist(predict(m3), main = "Rating Distribution", xlab = "Rating")
```




# Histograms (Comparing model using Tackle vs Tackle Percentage Won)

```{r}
hist(m3_3$residuals, main="No Starts Perc", xlab="Residual")

#model with tackle perc + SM
hist(m3$residuals, main = "StartsPerc", xlab = "Residual")
```










```{r}
#Model with tackles
plot(m3_3$residuals ~ m3_3$fitted.values, xlab = "Predicted Ratings", ylab = "Residual", data = defendars)
abline(h = 0)

#model with tackle perc + SM
plot(m3$residuals ~ m3$fitted.values, xlab = "Predicted Ratings", ylab = "Residual", data = defendars)
abline(h = 0)

```













































# World Cup 

```{r}
C45 <- read_excel("data.xlsx")
```


```{r}
model4 <- lm( Rating ~  Gls...11 + Ast...12 + Min + factor(Squad)-1, data = C45)
summary(model4)
```




```{r}
fe_coefs5 <- summary(model4)$coefficients
fe_coefs5 <- as.data.frame(fe_coefs5)
fe_coefs5[order(fe_coefs5$Estimate, decreasing = TRUE),]
```


```{r}
model4$fit
```

# Ronaldo is rated 88 and Messi is 91!